\textbf{Using the MSU Thesis Class}

### 2022-08-19 docs/msu-thesis.tex
v3.5b changed default value for \setabstractnamespace; updated docs and maketds

\def\msuversion{3.5}
\def\msudate{2022/08/15}
\title{\textbf{Using the MSU Thesis Class}}
\author{\textbf{Alan Munn}\\Department of Linguistics, Languages, and Cultures\\Michigan State University\\\texttt{\href{mailto:amunn@msu.edu}{amunn@msu.edu}}}
\date{Version \msuversion\\\msudate}
\usepackage{fontspec}
\usepackage[lmargin=.75in,rmargin=.75in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{titling}
\usepackage{array, booktabs, multicol, fancyhdr, xspace,tabularx}
\usepackage{enumitem}
\usepackage{fancyvrb,listings,url}
\usepackage[sf,small]{titlesec}
\usepackage[section]{placeins}
\usepackage[colorlinks=true]{hyperref}
\setmonofont{Inconsolatazi4}

@@

In addition to any options passed to the \pkg{memoir}\ class (e.g. |oldfontcommands|; see Section \ref{sec:fonts}, font size), the \pkg{msu-thesis}\ takes six options: one to specify the type of degree, (see Table~\ref{degrees}), one to enable landscape page numbering, two to enable per-chapter bibliographies and appendices, two to make small adjustments to  Table of Contents.  If no degree option is specified, a Ph.D. dissertation is assumed.

@@

Use the command |\setabstractnamespace| to change the spacing after the author name in the abstract. This command takes a value typically between 0 and 1 where 0 reduces the space to a single baselineskip, while 1 adds an extra baselineskip. The default is set to 1, but if that’s too large, try 0.5 or 0 as needed.

>>>>

\def\msuversion{3.5b}
\def\msudate{2022/08/19}
\title{\textbf{Using the MSU Thesis Class}}
\author{\textbf{Alan Munn}\\Department of Linguistics, Languages, and Cultures\\Michigan State University\\\texttt{\href{mailto:amunn@msu.edu}{amunn@msu.edu}}}
\date{Version \msuversion\\\msudate}
\usepackage{fontspec}
\usepackage[lmargin=.75in,rmargin=.75in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{titling}
\usepackage{array, booktabs, multicol, fancyhdr, xspace,tabularx}
\usepackage{enumitem}
\usepackage{fancyvrb,listings,url}
\usepackage[sf,small]{titlesec}
\usepackage[section]{placeins}
\usepackage[colorlinks=true]{hyperref}
\setmonofont{Inconsolatazi4}

@@

In addition to any options passed to the \pkg{memoir}\ class (e.g. |oldfontcommands|; see Section \ref{sec:fonts}, font size), the \pkg{msu-thesis}\ class takes six options: one to specify the type of degree, (see Table~\ref{degrees}), one to enable landscape page numbering, two to enable per-chapter bibliographies and appendices, two to make small adjustments to  Table of Contents.  If no degree option is specified, a Ph.D. dissertation is assumed.

@@

Use the command |\setabstractnamespace| to change the spacing after the author name in the abstract (and the public abstract, if present). This command takes a value typically between -1 and  and 1 where 0 reduces the space to a single baselineskip, while 1 adds an extra baselineskip. The default is set to 0. Depending on their mood at the time they check your thesis, the thesis office may want more or less space here, so use this command only to satisfy their bureaucratic self-importance.
